Imposed form in the Early Acheulean? Evidence from Gona, Afar, Ethiopia

### 2023-04-07 manuscript/manuscript.Rmd
updated the method section based on Dietz's slides.

>>>>

PCA on GM-transformed caliper measures (length, 3 breadth, 3 thickness). Length is maximum dimension, piece oriented so that Br1>Br3

Typological and technological attributions considered unreliable. Data grouped according to context (~2.5 mya Oldowan sites vs. ~1.5 mya Acheulean sites) and blank form (cobble, flake, indeterminant).

Associations between form and reduction intensity are considered as an indicator of “imposed form.” Such form could reflect mental templates and/or biased flaking patterns due to functional or technological constraints
